Andres Karjus

### 2018-12-06 index.Rmd
clis talk slides
moved items

### New things

* [Slides](https://andreskarjus.github.io/evoforces_cletalk/slides.html) of the talk _Challenges in detecting evolutionary forces in language change using diachronic corpora_ presented at the [CLE](http://www.lel.ed.ac.uk/cle/) seminar series, 06.11.2018 | paper preprint now also on [arXiv](http://arxiv.org/abs/1811.01275) | [code](https://github.com/andreskarjus/wfsim_fit)

@@

- The inaugural meeting of the Society for Computation in Linguistics, part of [LSA 2018](https://www.linguisticsociety.org/event/lsa-2018-annual-meeting) | download [poster](scilposter_sizeA1.pdf)
- [Edinburgh Language Lunch](http://groups.inf.ed.ac.uk/langlunch/)
- [Evolang 2018](http://evolang.cles.umk.pl) | [slides](https://drive.google.com/open?id=10az7BOV_tT-mAwMZXDoguKmZeTErnfzB) | open-access [proceedings](http://evolang.org/torun/proceedings/papertemplate.html?p=117) 
- [Applications in Cultural Evolution: Arts, Languages, Technologies](https://cultevol.ut.ee/) | _Selection above the baseline: quantifying the advection effect in four domains of cumulative culture_ | [slides](https://andreskarjus.github.io/cultevol_tartu_slides) with interactive data&plots | [code](https://github.com/andreskarjus/cultural_advection_Tartuce)
- New directions in language evolution research workshop, at the [SLE 2018](http://sle2018.eu/) | _Two problems and solutions in evolutionary corpus-based language dynamics research_ [slides](https://andreskarjus.github.io/sle_tallinn_languagedynamics) with interactive plots | [code](https://github.com/andreskarjus/sle_tallinn_languagedynamics)
- University of Edinburgh [Centre for Language Evolution](http://www.lel.ed.ac.uk/cle/) seminar series | _Challenges in detecting evolutionary forces in language change using diachronic corpora_ | [slides](https://andreskarjus.github.io/evoforces_cletalk/slides.html) | [code](https://github.com/andreskarjus/wfsim_fit)

>>>>

@@

- The inaugural meeting of the Society for Computation in Linguistics, part of [LSA 2018](https://www.linguisticsociety.org/event/lsa-2018-annual-meeting) | download [poster](scilposter_sizeA1.pdf)
- [Edinburgh Language Lunch](http://groups.inf.ed.ac.uk/langlunch/)
- [Evolang 2018](http://evolang.cles.umk.pl) | [slides](https://drive.google.com/open?id=10az7BOV_tT-mAwMZXDoguKmZeTErnfzB) | open-access [proceedings](http://evolang.org/torun/proceedings/papertemplate.html?p=117) 
- [Applications in Cultural Evolution: Arts, Languages, Technologies](https://cultevol.ut.ee/) | _Selection above the baseline: quantifying the advection effect in four domains of cumulative culture_ | [slides](https://andreskarjus.github.io/cultevol_tartu_slides) with interactive data&plots | [code](https://github.com/andreskarjus/cultural_advection_Tartuce)
- New directions in language evolution research workshop, at the [SLE 2018](http://sle2018.eu/) | _Two problems and solutions in evolutionary corpus-based language dynamics research_ [slides](https://andreskarjus.github.io/sle_tallinn_languagedynamics) with interactive plots | [code](https://github.com/andreskarjus/sle_tallinn_languagedynamics)
- University of Edinburgh [Centre for Language Evolution](http://www.lel.ed.ac.uk/cle/) seminar series | _Challenges in detecting evolutionary forces in language change using diachronic corpora_ | [slides](https://andreskarjus.github.io/evoforces_cletalk/slides.html) | [code](https://github.com/andreskarjus/wfsim_fit)
- Corpus Linguistics in Scotland Network Meeting, _Topical Fluctuations and Lexical Interactions in Diachronic Corpora_
-  [CLE](http://www.lel.ed.ac.uk/cle/) seminar series, 06.11.2018, _Challenges in detecting evolutionary forces in language change using diachronic corpora_ | [slides](https://andreskarjus.github.io/evoforces_cletalk/slides.html)
